Enforced Invariant Confluence

### 2018-09-19 doc/paper/sections/evaluation.tex
Consequence of TPC-C not being iconfluent.
From reviewer 11:

> During the TPC-C discussion, you should complete the description and
> let the reader know what it the implication of the sequence and unique
> identifiers being not invariant means for running that workload.

This commit tries to clarify the consequence of TPC-C not being
invariant confluent.

  % \item
    Two of the twelve invariants involve generating \textbf{sequential and
    unique identifiers}. Consider, for example, invariant 2 which dictates that
    a district's next order id \ttt{D\_NEXT\_O\_ID} is equal to the maximum
    order id \ttt{O\_ID} of orders within the district. The New Order
    transaction places an order with \ttt{O\_ID} equal to the current value of
    \ttt{D\_NEXT\_O\_ID} and then increments \ttt{D\_NEXT\_O\_ID}.
    We model this workload with an integer for \ttt{D\_NEXT\_O\_ID} and a map
    for \ttt{O\_ID} that maps order ids to order.
    %
    % We model this workload with three objects. \ttt{D\_NEXT\_O\_ID} is modeled
    % as an integer merged by $\max$. The order table is modelled as two objects.
    % The first is a set of all order ids used, merged by union. The second is a
    % map which maps order id to order. The map's merge function performs an
    % id-by-id merge of orders. If two different orders have the same id, the
    % merge function replaces them with a distinguished value to indicate that
    % the primary key constraint has been violated.
    %
    We applied Lucy to this workload and in less than a second, it produced a
    counterexample that---when labelled as reachable---confirms that the
    workload is \emph{not} \invariantconfluent{}~\cite{bailis2014coordination}.
% \end{enumerate}

>>>>

  % \item
    Two of the twelve invariants involve generating \textbf{sequential and
    unique identifiers}. Consider, for example, invariant 2 which dictates that
    a district's next order ID \ttt{D\_NEXT\_O\_ID} is equal to the maximum
    order id \ttt{O\_ID} of orders within the district. The New Order
    transaction places an order with \ttt{O\_ID} equal to the current value of
    \ttt{D\_NEXT\_O\_ID} and then increments \ttt{D\_NEXT\_O\_ID}.
    We model this workload with an integer for \ttt{D\_NEXT\_O\_ID} and a map
    for \ttt{O\_ID} that maps order IDs to order.
    %
    % We model this workload with three objects. \ttt{D\_NEXT\_O\_ID} is modeled
    % as an integer merged by $\max$. The order table is modelled as two objects.
    % The first is a set of all order ids used, merged by union. The second is a
    % map which maps order id to order. The map's merge function performs an
    % id-by-id merge of orders. If two different orders have the same id, the
    % merge function replaces them with a distinguished value to indicate that
    % the primary key constraint has been violated.
    %
    We applied Lucy to this workload and in less than a second, it produced a
    counterexample that---when labelled as reachable---confirms Bailis et al.'s
    finding that the workload is \emph{not}
    \invariantconfluent{}~\cite{bailis2014coordination}. Thus, the TPC-C
    benchmark requires some form of coordination to ensure unique and
    sequential IDs. Alternatively, as Bailis et al. describe
    in~\cite{bailis2014coordination}, the workload can be run coordination free
    if we drop the requirement that IDs are assigned sequentially.
% \end{enumerate}
